%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\textcolor{awesome}{\raisebox{0.1\height}{\faBriefcase\thinspace}}\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead DevOps Consultant} % Job title
    {Global Payments} % Organization
    {Atlanta, USA} % Location
    {August 2023 - October 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the infrastructure migration from Google App Engine to Google Kubernetes Engine, migrating over 100 Linux-based applications and transforming them into containerized microservices to achieve significant cost savings and enhanced performance.}
        \item {Architected and executed the migration strategy, delivering documentation, diagrams, and evidence to secure the necessary approvals and ensure a seamless transition.}
        \item {Designed and managed Cloud Build and Cloud Deployment pipelines, automating the build and deployment process through various testing phases and promotions to higher environments.}
        \item {Configured and maintained GKE clusters, routes, firewalls, and WAF, as well as associated pods and services, to optimize traffic handling for microservices.}
        \item {Optimized vCPU, memory, and horizontal autoscaling for both nodes and workloads, balancing performance and cost-effectiveness to preserve customer experience.}
        \item {Developed proactive alerting systems based on logs and metrics to notify the production support team of potential issues and ensure an appropriate response.}
        \item {Created handoff documentation for the DevOps, Production Support and Development teams.}
        \item {Utilized Google Cloud Platform (GCP) including Google Kubernetes Engine (GKE) (along with Anthos Service Mesh, Config Sync, Gateway API, and Istio), Cloud Build, Cloud Deploy, Google Artifact Registry (GAR), Cloud Logging, Cloud Metrics, Pub/Sub, Identity and Access Management (IAM), Google App Engine (GAE), Cloud SQL, Cloud Armor, Virtual Private Cloud, Cloud KMS, Secret Manager as well as others.}
        \item {Also used GitHub, Terraform, Kustomize (YAML), Scripting (Bash 85\%, Python 10\%, PowerShell 5\%), JFrog Artifactory, Java (Maven), and Jenkins (Groovy).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Solutions Engineer} % Job title
    {Levio (formerly Indellient)} % Organization
    {Oakville, Canada} % Location
    {May 2021 - August 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Used a multitude of technologies (including Chef, Terraform, Vault, AWS) on several clients of various sizes to design, create or update build, continuous integration, and continuous delivery systems with varying degrees of complexity.}
        \item {Interacted with clients at the business and software engineering levels to determine where their build process was facing issues.}
        \item {Created high- and low-level design diagrams and documentation explaining clients' current pain points, and the recommendations to fix them.}
        \item {Helped with creating business milestones and customer success metrics, which would then translate over to development milestones, sprints and tickets}
        \item {Developed code to create or upgrade build systems which was well tested and verifiable using DevOps best practices and principles - canary pipelines, blue/green deployments, least intrusive builds, etc.}
        \item {Had regular check in calls with clients to discuss progress, blockers and timeline.}
        \item {Once development was complete, had hand off meetings and provided demos and documentation of all work done.}
        \item {Regularly communicated with clients after project completion to make sure that code was still working as expected.}
        \item {Mentored and assisted less experienced DevOps engineers both in company and working for clients.}
        \item {In several small projects lasting a combined total of 1.5 years, utilized Amazon Web Services (AWS) including Amazon Elastic Compute Cloud (EC2), CodeBuild, CodeDeploy, Simple Storage Service (S3), Virtual Private Cloud (VPC), CloudWatch, and Secrets Manager.}
        \item {In a project lasting 3 months, utilized Vagrant, Chef (Ruby), GitHub, GitHub Actions (YAML), and Scripting (Bash 50\%, PowerShell 50\%).}
        \item {In a project lasting 1 year, utilized OpenShift, Terraform, Chef (Ruby), Vault, GitHub, JFrog Artifactory, Jenkins (Groovy), Scripting (Bash 80\%, Python 20\%), and Google Cloud Project (GCP) including Google Compute Engine (GCE), Google Cloud Storage (GCS), Virtual Private Cloud (VPC), and Cloud Logging.}
        \item {In a project lasting 6 months, utilized GitHub, Chef (Ruby), Ruby, and Microsoft Azure including Azure DevOps.}
        \item {In a project lasting 6 months, utilized Rancher, Terraform, Vault, GitLab (including CI/CD, SAST, DAST, etc.), Ansible, Java (Maven), JFrog Artifactory, and Scripting (Bash 80\%, Python 20\%).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer} % Job title
    {Global Payments (formerly Cayan)} % Organization
    {Boston, USA} % Location
    {Aug 2014 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Increased release cadence from biweekly to twice daily, through modifications and improvements to PowerShell, Chef, Hyper-V, and Failover Cluster commands and actions.}
        \item {Changed the Engineering Lab from one that was rigidly relying on an evaluation of SCVMM and had a single point of failure, to one that was easily able to recover from common error scenarios and in catastrophic cases, could be brought back up from scratch within 3 hours.}
        \item {Interviewed and trained two senior release engineers and a release engineer on the systems, as well as best practices and principles for DevOps.}
        \item {Was contacted by parent company to lead sibling companies towards Windows-based DevOps best practices, to present some of the experience I'd gained, and to show how we had accomplished certain automated tasks.}
        \item {Took lead on designing, creating a proof of concept, and implementing OpenStack, a private virtual cloud, inside our datacenter for our parent/sibling companies, which would allow each company portions of the datacenter, along with the tools needed to administer each of them adequately.}
        \item {Used Chef and Vagrant to create an IaaS setup, which could be easily re-instantiated quickly.}
        \item {Designed and created a highly available and scalable reverse proxy system which helped other developers access different iterations and versions of our web applications quickly and easily through SNI, both for testing and verification.}
        \item {Utilized GitHub, Jenkins (Groovy), GoCD, Chef, Scripting (PowerShell 70\%, Bash 20\%, Python 10\%), JFrog Artifactory, Microsoft Hyper-V, OpenStack, Microsoft SQL Server, and C\# .NET (NAnt / MSBuild).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.Net Software Engineer} % Job title
    {Credit Suisse (via Infusion)} % Organization
    {London, UK} % Location
    {Sep 2012 - Aug 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed, tested and debugged a workflow-based application for improved EPE on defaults for the bank using Agile methodologies and following SOLID principles to create an architecturally strong and scalable application, from conception through to production.}
        \item {Actively involved in code reviews, sprint retrospectives, library assessment meetings and daily standups for status reports and knowledge sharing.}
        \item {Improved coworkers and fellow teammates previously implemented code using proven coding practices – MVVM, SOLID principles, TDD, Pair-Programming, and IoC.}
        \item {Utilized Jenkins, C\# .NET, Microsoft SQL Server, Subversion, and Scripting (PowerShell).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior .Net Software Engineer} % Job title
    {Radix} % Organization
    {Windsor, Canada} % Location
    {Aug 2011 - Aug 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed, maintained and debugged several database-heavy applications in C\# WinForms, for many clients simultaneously.}
        \item {Experimented with different programming suites to find the best software to use with each project.}
        \item {Tasked with meeting clients, assessing their needs, developing a time schedule for release that was realistic and acceptable, and under certain circumstances developing quick demos onsite.}
        \item {Frequently gave feedback during several meetings regarding program requirements and feasibility.}
        \item {Built small code libraries for interacting with Serial Port based robotic equipment.}
        \item {Utilized C\# .NET, MySQL, Subversion, and Scripting (PowerShell).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
